[WIP] Church Bells are Not Ringing: Decrease in the Opposite-Sex and Same-Sex Couples Opting for Religous Marriage Ceremonies in England and Wales

### 2024-04-24 paper/paper.qmd
paper update

## Data Description
The data sets for same and opposite-sex couples were derived from the *Office for National Statistics in the United Kingdom* with the 2020 edition of the “Marriages in England and Wales” workbook as raw data. This data is collected at the time a marriage is registered as part of civil registration which is a legal requirement in completing a legally recognized marriage in England and Wales. Annual marriage statistics are available to the public approximately two years after the end of the reference year [@statsguide]. Notably, same-sex couples that are currently in a civil partnership can have it converted to a marriage but these numbers are not counted towards the marriage statistics of same-sex couples in the workbook. The data collected and used in this paper is used to measure the number of couples that opt for civil or religious marriage ceremonies on a yearly basis [@statsguide]. By measuring marriage ceremony trends, it can help measure and provide insight onto greater social attitudes towards religion. Based on aforementioned literature about the perceived decline of religiosity in the United Kingdom, marriage ceremony data was chosen as a potential form of measuring this phenomena due to the historical link between marriage and religion [@marriagedeclineuk]. Since marriage is a significant life event, the presence and absence of religion in ceremonies can corroborate the decline of religiosity in individual life. These marriage ceremony entries in the "Marriages in England and Wales" workbook are a reflection of each couple's relationship with religion and whether or not it is strong enough to opt for a religious ceremony. Although the data set only reflects ceremony types, those entries were antedated by personal consideration of a couple's proximity to religion.

@@

Generally, the data from the *National Office of Statistics* was taken without any modifications to most of the selected columns. The notable exception to this would be in the opposite-sex couple dataset where the `approved_civil` column had values of `[z]` and `[x]` in the `other_religions` column when no data was available for a specific year. Since this paper aimed to broadly look at a summary of religion in marriage ceremonies, these values were converted to 0s to continue calculating summary statistics for individual years. All of the values in both data sets were also converted from the character class to the numeric class which is a divergence from the original workbook produced by the *National Office of Statistics*. This decision was made to aid in calculating and graphing the data as there were no values that could not be converted to numeric aside from the two cases mentioned above.

>>>>

## Data Description
The data sets for same and opposite-sex couples were derived from the *Office for National Statistics in the United Kingdom* with the 2020 edition of the “Marriages in England and Wales” workbook as raw data. This data is collected at the time a marriage is registered as part of civil registration which is a legal requirement in completing a legally recognized marriage in England and Wales. Annual marriage statistics are available to the public approximately two years after the end of the reference year [@statsguide]. Notably, same-sex couples that are currently in a civil partnership can have it converted to a marriage but these numbers are not counted towards the marriage statistics of same-sex couples in the workbook. The data collected and used in this paper is used to measure the number of couples that opt for civil or religious marriage ceremonies on a yearly basis [@statsguide].

By measuring marriage ceremony trends, it can help measure and provide insight onto greater social attitudes towards religion. Based on aforementioned literature about the perceived decline of religiosity in the United Kingdom, marriage ceremony data was chosen as a potential form of measuring this phenomena due to the historical link between marriage and religion [@marriagedeclineuk]. Since marriage is a significant life event, the presence and absence of religion in ceremonies can corroborate the decline of religiosity in individual life. These marriage ceremony entries in the "Marriages in England and Wales" workbook are a reflection of each couple's relationship with religion and whether or not it is strong enough to opt for a religious ceremony. Although the data set only reflects ceremony types, those entries were antedated by personal consideration of a couple's proximity to religion.

@@

Generally, the data from the *National Office of Statistics* was taken without any modifications to most of the selected columns. The notable exception to this would be in the opposite-sex couple dataset where the `approved_civil` column had values of `[z]` and `[x]` in the `other_religions` column when no data was available for a specific year. Since this paper aimed to broadly look at a summary of religion in marriage ceremonies, these values were converted to 0s to continue calculating summary statistics for individual years. All of the values in both data sets were also converted from the character class to the numeric class which is a divergence from the original workbook produced by the *National Office of Statistics*. This decision was made to aid in calculating and graphing the data as there were no values that could not be converted to numeric aside from the two cases mentioned above. Samples of the cleaned datasets produced are seen in @tbl-opposite and @tbl-same.

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-opposite
#| tbl-cap: Sample of Cleaned Opposite-Sex Marriage Ceremony Data

# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd

head (opposite_sex, 5) |>
  kable(
    col.names = c("Year","Total Marriages","All Civil", "Approved Civil", "All Religious", "Church of England", "Roman Catholic", "Other Christian Denominations", "Other Religions"),
  booktabs = TRUE
  )
```

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-same
#| tbl-cap: Cleaned Same-Sex Marriage Ceremony Data

# Code referenced from: https://github.com/InessaDeAngelis/Toronto_Elections/blob/main/outputs/paper/toronto_elections_paper.qmd

head (same_sex) |>
  kable(
    col.names = c("Year","Total Marriages","Male", "Female", "All Civil", "Approved Civil", "All Religious"),
  booktabs = TRUE
  )
```
